---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# shiny for accessing to clean fuels for cooking vs gdp per capita


## Siyi Li (29018102)

In this shinyapp, the package is used including: **shiny**, **plotly**, **tidyverse**, **crosstalk**, **DT**, **ggplot2**

Please install all this package before you visit the shinyapp.


```{r, eval = FALSE}
install.packages(c("shiny", "crosstalk", "plotly", "DT", "tidyverse", "here","ggplot2"))
```

## How to run the app

- About the **chart** session, which shows the access to the fuels for cooking and GDP per capita.

On the upper left of the chart, you can click the **Linearize x-axis** to get the different chart which has the linear x-axis (the value on the x-axis without the log10 transformation).

On the upper right of the chart, you could click **Hide countries < 1 million** to filter out the countries which has population size less than 1 million.

On the middle, you could find a box which has the lable **Which country do you want to analyze**, you can select one or more countries and get their information.

On the bottom of the chart, you also can find a time bar, you can move the circle button to see the points in different years.

Finally, you can click each point to get more details.


-  About the **table** session, you can click the top of the table button to get the whole dataset.

The table contains the variables like continent, country, code, year, new_cooking, new_gdp_per_capita and population. in each variable column, you could sort the variable with decreasing or incresing order.

You also can search something that you are interested in.


-  About the **about** session, you can find more information from the source link, and you can find my Github from the Github link.



## Session Information

The session info is:

```{r session-info}
 sessioninfo::session_info()
```
